\documentclass{article}
\usepackage{amsmath, amssymb, graphicx}

\begin{document}

\title{Analysis of Function Transformations}
\author{}
\date{}
\maketitle

\section{Introduction}
Given the function $f(x)$ depicted in Figure 4, we analyze and derive the transformations leading to the graphs shown in Figures 5 through 8. Each transformation is considered in detail with its analytical properties and effects on the function.

\section{Absolute Value Transformation: $f_1(x) = |f(x)|$}
The function $f_1(x) = |f(x)|$ modifies the original function such that all negative values of $f(x)$ are reflected above the $x$-axis. Mathematically, we define:
\[
f_1(x) = \begin{cases} 
    f(x), & \text{if } f(x) \geq 0, \\
    -f(x), & \text{if } f(x) < 0.
\end{cases}
\]
This operation does not alter the domain of the function but ensures that all function values remain non-negative. The points where $f(x) = 0$ remain unchanged.\newline
\textbf{Correct Answer: Yes}

\section{Reflection Across the x-axis: $f_2(x) = -f(x)$}
The transformation $f_2(x) = -f(x)$ reflects the graph of $f(x)$ across the $x$-axis. This operation affects all function values by negating them:
\[
f_2(x) = -f(x) \quad \forall x.
\]
Zeros of the function remain unchanged, while positive values become negative and vice versa.\newline
\textbf{Correct Answer: Yes}

\section{Even Function Extension: $f_3(x) = f(|x|)$}
Applying $f_3(x) = f(|x|)$ modifies the function by making it symmetric with respect to the $y$-axis. Mathematically,
\[
f_3(x) = \begin{cases} 
    f(x), & \text{if } x \geq 0, \\
    f(-x), & \text{if } x < 0.
\end{cases}
\]
This operation preserves function values for $x \geq 0$ but mirrors them into the negative $x$ region. However, based on the given figures, this transformation does not match the expected graph.\newline
\textbf{Correct Answer: No}

\section{Reflection Across the y-axis: $f_4(x) = f(-x)$}
The transformation $f_4(x) = f(-x)$ reflects the graph across the $y$-axis, which means:
\[
f_4(x) = f(-x) \quad \forall x.
\]
This preserves function values symmetrically but swaps left and right sides.\newline
\textbf{Correct Answer: Yes}

\section{Conclusion}
Each of these transformations provides a fundamental way to manipulate functions, preserving key properties such as symmetry, zeros, and behavior under reflection. Understanding these modifications is essential in various applications of mathematical analysis and function modeling.

\end{document}
