\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\begin{document}

\section*{Triangle Analysis in Square $ABCD$}

Given a square $ABCD$ with points $E$ and $F$ being the midpoints of sides $AD$ and $CD$ respectively, and point $G$ being the intersection of segments $CE$ and $BF$, we will analyze the properties of triangles $CDG$, $ADG$, $ABG$, and $BCG$.

\subsection*{Step-by-Step Analysis}

\subsubsection*{1. Coordinates Assignment}
Let the vertices of square $ABCD$ be:
\[
A(0, 1), \quad B(1, 1), \quad C(1, 0), \quad D(0, 0)
\]
The midpoints $E$ and $F$ are calculated as follows:
\[
E\, \text{(midpoint of $AD$)}: \quad E\left( \frac{0 + 0}{2}, \frac{1 + 0}{2} \right) = E(0, 0.5)
\]
\[
F\, \text{(midpoint of $CD$)}: \quad F\left( \frac{1 + 0}{2}, \frac{0 + 0}{2} \right) = F(0.5, 0)
\]

\subsubsection*{2. Finding the Intersection Point $G$}
The line segment $CE$ can be determined using the coordinates of $C$ and $E$:
\[
\text{Slope from $C(1, 0)$ to $E(0, 0.5)$}: \quad \text{slope} = \frac{0.5 - 0}{0 - 1} = -0.5
\]
Using point-slope form, the equation of line $CE$ is:
\[
y - 0 = -0.5(x - 1) \implies y = -0.5x + 0.5
\]

For segment $BF$ from $B(1, 1)$ to $F(0.5, 0)$:
\[
\text{Slope}: \quad \frac{0 - 1}{0.5 - 1} = 2
\]
Its equation is:
\[
y - 1 = 2(x - 1) \implies y = 2x - 1
\]

To find $G$, solve the equations:
\[
-0.5x + 0.5 = 2x - 1
\]
\[
2.5x = 1.5 \implies x = 0.6
\]
Substituting $x$ back to find $y$:
\[
y = 2(0.6) - 1 = 0.2
\]
Thus, $G(0.6, 0.2)$.

\subsection*{Analyzing the Triangles}

\paragraph{a) Triangle $CDG$ is Isosceles}
The lengths $CD$, $CG$, and $DG$ need to be compared.
\[
CD = 1, \quad CG = \sqrt{(1 - 0.6)^2 + (0 - 0.2)^2} = \sqrt{0.16 + 0.04} = \sqrt{0.2}, \quad DG = \sqrt{(0 - 0.6)^2 + (0 - 0.2)^2} = \sqrt{0.36 + 0.04} = \sqrt{0.4}
\]
Since $CG$ and $DG$ are not equal, triangle $CDG$ is not isosceles. \textbf{Answer: No.}

\paragraph{b) Triangle $ADG$ is Right}
Check if the slopes of $AD$ and $AG$ are negative reciprocals.
\[
\text{Slope of $AD$} = 0 \quad \text{(horizontal line)}, \quad \text{Slope of $AG$} = \frac{0.2 - 1}{0.6 - 0} = \frac{-0.8}{0.6} = -\frac{4}{3}
\]
Since they are not negative reciprocals, $ADG$ is not a right triangle. \textbf{Answer: No.}

\paragraph{c) Triangle $ABG$ is Isosceles}
Compare lengths $AB$, $AG$, and $BG$:
\[
AB = 1, \quad AG = \sqrt{(0.6 - 0)^2 + (0.2 - 1)^2} = \sqrt{0.36 + 0.64} = \sqrt{1} = 1, \quad BG = \sqrt{(0.6 - 1)^2 + (0.2 - 1)^2} = \sqrt{0.16 + 0.64} = \sqrt{0.8} \neq 1
\]
Since $AB = AG$, triangle $ABG$ is isosceles. \textbf{Answer: Yes.}

\paragraph{d) Triangle $BCG$ is Right}
Check slopes of $BC$ and $BG$:
\[
\text{Slope of $BC$} = \frac{0 - 1}{1 - 1} \quad \text{(undefined, vertical line)}
\]
\[
\text{Slope of $BG$} = \frac{0.2 - 1}{0.6 - 1} = \frac{-0.8}{-0.4} = 2
\]
Since one slope is undefined (vertical line) and the other is defined, triangle $BCG$ is a right triangle. \textbf{Answer: Yes.}

\subsection*{Summary of Results}
\begin{itemize}
    \item Triangle $CDG$ is isosceles: \textbf{No.}
    \item Triangle $ADG$ is right: \textbf{No.}
    \item Triangle $ABG$ is isosceles: \textbf{Yes.}
    \item Triangle $BCG$ is right: \textbf{Yes.}
\end{itemize}

\end{document}
